%%
%% Resume of Michael Belousov
%% feel free to copy as much as you'd like.
%%
%% The LaTeX itself does the job.
%% Future commits will improve on the formatting
%%

\documentclass[Letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage[empty]{fullpage}
\usepackage[pdftex]{hyperref}
\usepackage[tmargin=0.5in,margin=0.6in]{geometry}
\usepackage{multicol}
\usepackage{mdwlist}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{-0.8em}{-0.8em}
\titlespacing{\subsection}{0pt}{-0.8em}{-0.8em}
\titlespacing{\subsubsection}{0pt}{-0.8em}{-0.8em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom Commands

\newcommand{\bul}{$\blacktriangleright$ }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\pagenumbering{gobble}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\setlength{\parsep}{1em}
\setlength{\itemsep}{0.2em}
\setlength{\headsep}{0.2em}
\setlength{\topskip}{0.2em}
\setlength{\topmargin}{0.2em}
\setlength{\topsep}{0.2em}
\setlength{\partopsep}{0.2em}
\setlength{\columnsep}{1em}
%\setlength{\columntopskip}{0em}

\addtolength{\topmargin}{-4em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
\textbf{\href{mailto:michael.belousov98@gmail.com}{\Large Michael Belousov}}\\
\href{mailto:michael.belousov98@gmail.com}{michael.belousov98@gmail.com}\\
Mobile : (203) 502-9425\\
\href{https://MichaelBelousov.github.io/}{\texttt{https://MichaelBelousov.github.io}} $\gets$ I have a small blog, check it out\\
\hrule
\vspace{1em} % HACCCCK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Objective}

Merit an innovative software engineering position employing complex problem solving, and team initiative.


\vspace{-1em} % HACCCCK
\begin{multicols}{2}

    \section*{Education}

        \textsc{University of Connecticut}, Storrs, CT\\
        \textit{Bachelor of Science}, Computer Science and Engineering, anticipated May 2019\\
        GPA 3.7, on track to graduate at the end of third year.
    
    \subsubsection*{Notable Courses}
    
        Algorithms and Complexity\\
        Theory of Computation\\
        Modern C++ Programming (the most fun CSE class at UCONN) \\
        Probabilistic Performance of Computer Programs
        
\end{multicols}

\vspace{-1.5em} % HACCCCK
\section*{Experience}
\vspace{0.1em}

    \textsc{Bentley Systems},
    \textit{Software Engineering Intern}\\
    May 2018-- August 2018\\
        \bul Tested and implemented algorithms (Visvalingam \& Whyatt, Ramer-Douglas-Peucker) 
        for intelligent curve fitting of various functions over elevation data in 
        drainage system simulation.
        \\
        \bul Implemented a React web front-end and ASP.NET-core back-end wrapping a C\# desktop 
        application for estimating emergency preparedness in pipe systems with an intuitive 
        slippy map interface.
        \\
        \bul Lead exploration of new technologies (e.g. Redux) for which Bentley Systems
        had no established conventions.

    \textsc{ITS},
    \textit{Security Analyst and Developer}\\
    December 2016--\textit{Current}\\
        \bul Developed solutions and web applications for analyzing, maintaining, and automating UCONN network security.
        \\
        \bul Upgraded a PHP-Python2 XMLRPC + jQuery web stack into bilingual Python3 
        with configurable boilerplate code generation.
        \\
        \bul Built Python packaging into the development environment with git and 
        dependency management.
        \\
        \bul Created an SVG network diagramming toolset using SNMP, CDP/LLDP scanning, 
        and a sophisticated CISCO router CLI parser.

    \textsc{UCONN Speech and Hearing research},
    \textit{Sole Application Developer and IT Consultant}\\
    March 2017--July 2018\\
        \bul Created interactive simulation software (a game in Unreal Engine 4) 
        for navigation tracking in neurological research, as the sole developer.
        \\
        \bul Built a TkInter Python app for top-down playback of participant navigation,
        and as a GUI to a data and statistics aggregator for participant data.
        
\begin{multicols}{2}

    \subsection*{Technological Competencies}

        C++, Python, C, GNU/Linux+Bash, git, gitlab, vim, \\
        TypeScript, React, Node.js, GLSL, C\#+ASP.NET, \\
        Webpack, Java, HTML5, JavaScript, [postgre]SQL, \\ 
        PHP, Bootstrap, CSS+sass/scss, Splunk, \LaTeX, lisp \\

    \subsection*{Skills}

        Presentation, Mentoring\\
        Graphics, Visualization, Office Suites, Automation\\
        3D Modeling and design for optimized rendering

\end{multicols}

\section*{Hobbies and Extracurricular}

    \bul Upsilon Pi Epsilon member, the computing honor society\\
    \bul 3D Art, procedural (computer-generated) art and animation\\
    \bul Also: reading, writing, filming, casual gaming, C++ template meta-programming

\clearpage

\end{document}